Selección de Instancias

### 2015-05-04 doc/paper.tex
* Added stop condition * worked on paper

\documentclass[11pt]{article}
\usepackage{paper}
\usepackage{times}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{url}
\usepackage{latexsym}
\usepackage[utf8]{inputenc}

@@

\section{Función de evaluación}
En [referencia a cano] se describe una función de evaluación que considera la tasa de instancias clasificadas correctamente tomando en cuenta el conjunto reducido como conjunto de entrenamiento y una tasa de reducción del conjunto original. Se hace uso de una constante $\alpha$ donde $\alpha \in [0,1]$ para darle ponderación a ambos parámetros. La fórmula usada para medir la calidad de una solución es:

@@

El objetivo de un algoritmo es maximizar esta función, entonces si $evaluar(A) < evaluar(B)$, se tiene que $B$ es mejor solución que $A$. Para los experimentos se usó la tasa sugerida por [referencia a cano] de $\alpha = 0.5$ dándole la misma ponderación a $tasa\_clas$ y a $porcen\_redc$.

@@

@@

\subsection{Operador}
Ante la necesidad de movernos en el
espacio de busqueda, surge la idea de un operador 
que modifique de manera sutil (y rápida) una solución
dada. 
En nuestro caso, nuestro operador selecciona al
azar un bit ``prendido'' y lo ``apaga'', que se traduce
en ``sacar'' una instancia del conjunto de instancias solución.

De esta manera, se consiguen soluciones cada vez más pequeñas y una tasa
de aciertos $tasa\_clas$ cada vez más precisas: esto viene de si tenemos 
$x$ aciertos y $w$ instancias que no están en la solución, aumetar el tamaño
de una solución conllevaría a una posible $tasa\_clas = x / (w - 1) $,
que supondría una mayor $tasa\_clas$ y por lo tanto una mejor solución. Sin embargo, 
esto no puede estar más alejado de la realidad.

\subsection{Layout}
\label{ssec:layout}

Format manuscripts two columns to a page, in the manner these
instructions are formatted. The exact dimensions for a page on A4
paper are:

\begin{itemize}
\item Left and right margins: 2.5 cm
\item Top margin: 2.5 cm
\item Bottom margin: 2.5 cm
\item Column width: 7.7 cm
\item Column height: 24.7 cm
\item Gap between columns: 0.6 cm
\end{itemize}

\noindent Papers should not be submitted on any other paper size.
 If you cannot meet the above requirements about the production of your electronic submission, please contact the publication chairs above as soon as possible.

\subsection{Fonts}

For reasons of uniformity, Adobe's {\bf Times Roman} font should be
used. In \LaTeX2e{} this is accomplished by putting

\begin{quote}
\begin{verbatim}
\usepackage{times}
\usepackage{latexsym}
\end{verbatim}
\end{quote}
in the preamble. If Times Roman is unavailable, use {\bf Computer
  Modern Roman} (\LaTeX2e{}'s default).  Note that the latter is about
  10\% less dense than Adobe's Times Roman font.

\begin{table}[h]
\begin{center}
\begin{tabular}{|l|rl|}
\hline \bf Type of Text & \bf Font Size & \bf Style \\ \hline
paper title & 15 pt & bold \\
author names & 12 pt & bold \\
author affiliation & 12 pt & \\
the word ``Abstract'' & 12 pt & bold \\
section titles & 12 pt & bold \\
document text & 11 pt  &\\
captions & 11 pt & \\
abstract text & 10 pt & \\
bibliography & 10 pt & \\
footnotes & 9 pt & \\
\hline
\end{tabular}
\end{center}
\caption{\label{font-table} Font guide. }
\end{table}

\subsection{The First Page}
\label{ssec:first}

Center the title, author's name(s) and affiliation(s) across both
columns. Do not use footnotes for affiliations. Do not include the
paper ID number assigned during the submission process. Use the
two-column format only when you begin the abstract.

{\bf Title}: Place the title centered at the top of the first page, in
a 15-point bold font. (For a complete guide to font sizes and styles,
see Table~\ref{font-table}) Long titles should be typed on two lines
without a blank line intervening. Approximately, put the title at 2.5
cm from the top of the page, followed by a blank line, then the
author's names(s), and the affiliation on the following line. Do not
use only initials for given names (middle initials are allowed). Do
not format surnames in all capitals (e.g., use ``Schlangen'' not
``SCHLANGEN'').  Do not format title and section headings in all
capitals as well except for proper names (such as ``BLEU'') that are
conventionally in all capitals.  The affiliation should contain the
author's complete address, and if possible, an electronic mail
address. Start the body of the first page 7.5 cm from the top of the
page.

The title, author names and addresses should be completely identical
to those entered to the electronical paper submission website in order
to maintain the consistency of author information among all
publications of the conference. If they are different, the publication
chairs may resolve the difference without consulting with you; so it
is in your own interest to double-check that the information is
consistent.

{\bf Abstract}: Type the abstract at the beginning of the first
column. The width of the abstract text should be smaller than the
width of the columns for the text in the body of the paper by about
0.6 cm on each side. Center the word {\bf Abstract} in a 12 point bold
font above the body of the abstract. The abstract should be a concise
summary of the general thesis and conclusions of the paper. It should
be no longer than 200 words. The abstract text should be in 10 point font.

{\bf Text}: Begin typing the main body of the text immediately after
the abstract, observing the two-column format as shown in 
the present document. Do not include page numbers.

{\bf Indent} when starting a new paragraph. Use 11 points for text and 
subsection headings, 12 points for section headings and 15 points for
the title.

\subsection{Sections}

{\bf Headings}: Type and label section and subsection headings in the
style shown on the present document.  Use numbered sections (Arabic
numerals) in order to facilitate cross references. Number subsections
with the section number and the subsection number separated by a dot,
in Arabic numerals. Do not number subsubsections.

{\bf Citations}: Citations within the text appear in parentheses
as~\cite{Gusfield:97} or, if the author's name appears in the text
itself, as Gusfield~\shortcite{Gusfield:97}.  Append lowercase letters
to the year in cases of ambiguity.  Treat double authors as
in~\cite{Aho:72}, but write as in~\cite{Chandra:81} when more than two
authors are involved. Collapse multiple citations as
in~\cite{Gusfield:97,Aho:72}. Also refrain from using full citations
as sentence constituents. We suggest that instead of
\begin{quote}
  ``\cite{Gusfield:97} showed that ...''
\end{quote}
you use
\begin{quote}
``Gusfield \shortcite{Gusfield:97}   showed that ...''
\end{quote}

If you are using the provided \LaTeX{} and Bib\TeX{} style files, you
can use the command \verb|\newcite| to get ``author (year)'' citations.

As reviewing will be double-blind, the submitted version of the papers
should not include the authors' names and affiliations. Furthermore,
self-references that reveal the author's identity, e.g.,
\begin{quote}
``We previously showed \cite{Gusfield:97} ...''  
\end{quote}
should be avoided. Instead, use citations such as 
\begin{quote}
``Gusfield \shortcite{Gusfield:97}
previously showed ... ''
\end{quote}

\textbf{Please do not use anonymous citations} and do not include
acknowledgements when submitting your papers. Papers that do not
conform to these requirements may be rejected without review.

\textbf{References}: Gather the full set of references together under
the heading {\bf References}; place the section before any Appendices,
unless they contain references. Arrange the references alphabetically
by first author, rather than by order of occurrence in the text.
Provide as complete a citation as possible, using a consistent format,
such as the one for {\em Computational Linguistics\/} or the one in the 
{\em Publication Manual of the American 
Psychological Association\/}~\cite{APA:83}.  Use of full names for
authors rather than initials is preferred.  A list of abbreviations
for common computer science journals can be found in the ACM 
{\em Computing Reviews\/}~\cite{ACM:83}.

The \LaTeX{} and Bib\TeX{} style files provided roughly fit the
American Psychological Association format, allowing regular citations, 
short citations and multiple citations as described above.

{\bf Appendices}: Appendices, if any, directly follow the text and the
references (but see above).  Letter them in sequence and provide an
informative title: {\bf Appendix A. Title of Appendix}.

\subsection{Footnotes}

{\bf Footnotes}: Put footnotes at the bottom of the page and use 9
points text. They may be numbered or referred to by asterisks or other
symbols.\footnote{This is how a footnote should appear.} Footnotes
should be separated from the text by a line.\footnote{Note the line
separating the footnotes from the text.}

\subsection{Graphics}

{\bf Illustrations}: Place figures, tables, and photographs in the
paper near where they are first discussed, rather than at the end, if
possible.  Wide illustrations may run across both columns.  Color
illustrations are discouraged, unless you have verified that  
they will be understandable when printed in black ink.

{\bf Captions}: Provide a caption for every illustration; number each one
sequentially in the form:  ``Figure 1. Caption of the Figure.'' ``Table 1.
Caption of the Table.''  Type the captions of the figures and 
tables below the body, using 11 point text.

\section{XML conversion and supported \LaTeX\ packages}

ACL 2014 innovates over earlier years in that we will attempt to
automatically convert your \LaTeX\ source files to machine-readable
XML with semantic markup. This will facilitate future research that
uses the ACL proceedings themselves as a corpus.

We encourage you to submit a ZIP file of your \LaTeX\ sources along
with the camera-ready version of your paper. We will then convert them
to XML automatically, using the LaTeXML tool
(\url{http://dlmf.nist.gov/LaTeXML}). LaTeXML has \emph{bindings} for
a number of \LaTeX\ packages, including the ACL 2014 stylefile. These
bindings allow LaTeXML to render the commands from these packages
correctly in XML. For best results, we encourage you to use the
packages that are officially supported by LaTeXML, listed at
\url{http://dlmf.nist.gov/LaTeXML/manual/included.bindings}

\section{Translation of non-English Terms}

It is also advised to supplement non-English characters and terms
with appropriate transliterations and/or translations
since not all readers understand all such characters and terms.
Inline transliteration or translation can be represented in
the order of: original-form transliteration ``translation''.

\section{Length of Submission}
\label{sec:length}

Long papers may consist of up to 9 pages of content, plus two extra
pages for references. Short papers may consist of up to 5 pages of
content, plus two extra pages for references.  Papers that do not
conform to the specified length and formatting requirements may be
rejected without review.

\section*{Acknowledgments}

The acknowledgments should go immediately before the references.  Do
not number the acknowledgments section. Do not include this section
when submitting your paper for review.

@@

\bibitem[\protect\citename{Aho and Ullman}1972]{Aho:72}
Alfred~V. Aho and Jeffrey~D. Ullman.
\newblock 1972.
\newblock {\em The Theory of Parsing, Translation and Compiling}, volume~1.
\newblock Prentice-{Hall}, Englewood Cliffs, NJ.

\bibitem[\protect\citename{{American Psychological Association}}1983]{APA:83}
{American Psychological Association}.
\newblock 1983.
\newblock {\em Publications Manual}.
\newblock American Psychological Association, Washington, DC.

\bibitem[\protect\citename{{Association for Computing Machinery}}1983]{ACM:83}
{Association for Computing Machinery}.
\newblock 1983.
\newblock {\em Computing Reviews}, 24(11):503--512.

\bibitem[\protect\citename{Chandra \bgroup et al.\egroup }1981]{Chandra:81}
Ashok~K. Chandra, Dexter~C. Kozen, and Larry~J. Stockmeyer.
\newblock 1981.
\newblock Alternation.
\newblock {\em Journal of the Association for Computing Machinery},
  28(1):114--133.

\bibitem[\protect\citename{Gusfield}1997]{Gusfield:97}
Dan Gusfield.
\newblock 1997.
\newblock {\em Algorithms on Strings, Trees and Sequences}.
\newblock Cambridge University Press, Cambridge, UK.

>>>>

\documentclass[11pt]{article}
\usepackage{paper}
\usepackage{times}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{multirow}
\usepackage{url}
\usepackage{latexsym}
\usepackage[utf8]{inputenc}

@@

\section{Función de evaluación}
En (Cano et. al 2003) se describe una función de evaluación que considera la tasa de instancias clasificadas correctamente tomando en cuenta el conjunto reducido como conjunto de entrenamiento y una tasa de reducción del conjunto original. Se hace uso de una constante $\alpha$ donde $\alpha \in [0,1]$ para darle ponderación a ambos parámetros. La fórmula usada para medir la calidad de una solución es:

@@

El objetivo de un algoritmo es maximizar esta función, entonces si $evaluar(A) < evaluar(B)$, se tiene que $B$ es mejor solución que $A$. Para los experimentos se usó la tasa sugerida por (Cano et. al 2003) de $\alpha = 0.5$ dándole la misma ponderación a $tasa\_clas$ y a $porcen\_redc$.

@@

    Como condición de parada se establece que el mínimo de calidad de una solución sea $0.95$ y una cantidad determinada de iteraciones en las cuales la solución no cambie.

@@

\section{Experimentos}

Se seleccionaron instancias de tamaño pequeño con menos de 1000 instancias y mediano con más de 1000 pero menos de 5000 instancias. Cada problema cuenta con atributos y clases en el dominio de los reales.

\subsection{Resultados}

 Se seleccionan tres casos pequeños y se observa que el porcentaje de reducción es pequeño.

\begin{table}[h]
\begin{tabular}{ |l|l|l|l| }
    \hline
    Caso & Instancias & Atributos & \% red. \\ \hline
    Haberman & 306 & 4 & 13.7 \\ \hline
    Heart & 270 & 14 & 46 \\ \hline
    Fertility & 100 & 10 & 34 \\ \hline
\end{tabular}
\caption{Datos pequeños}
\label{tabla:1}
\end{table}

    Para los casos medianos, se observa que el porcentaje de reducción es mucho mayor

\begin{table}[h]
\begin{tabular}{ |l|l|l|l| }
    \hline
    Caso & Instancias & Atributos & \% red. \\ \hline
    Phishing & 2456 & 31 & 84 \\ \hline
    Segment & 2310 & 20 & 87 \\ \hline
    Bank & 1372 & 5 & 90 \\ \hline
\end{tabular}
\caption{Datos medianos}
\label{tabla:2}
\end{table}

@@

\bibitem[\protect\citename{Cano et al}2003]{Cano:03}
José Ramón Cano, Francisco Herrera, and Manuel Lozano.
\newblock 2003.
\newblock {\em Using evo-
lutionary algorithms as instance selection for data reduction in kdd: an
experimental study.}.
\newblock Evolutionary Computation, IEEE Transactions.

\bibitem[\protect\citename{Toussaint}200]{Toussaint:02}
Godfried Toussaing.
\newblock 2002.
\newblock {\em Proximity Graphs for Nearest Neighbor Decision Problem}.
\newblock School of computer science. McGill University
